Discovering cell type motifs in connectomics data

### 2013-12-02 docs/paper.tex
substantial updates to including figures

\documentclass{article}
\usepackage[english,american]{babel}
\usepackage[disable]{todonotes}
\usepackage{subfiles}
\usepackage{grffile}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage[citestyle=authoryear,url=false,hyperref=auto,isbn=false]{biblatex}

\title{Discovering cell type motifs in connectomics data}
\author{Eric Jonas \\ Konrad Kording}

@@

\listoftodos

@@

\section{Introduction}
Emerging techniques (cite Lichtman, Zador, Denk etc) promise to
quantify the location of each neuron within a volume of interest,
along with its connections to all other neurons. Far exceeding the
capacity of neuroanatomists to trace small circuits, this leads to
enormous datasets that quantify aspects of the nervous system. The
rise of high-throughput sequencing techniques necessitated the
development of novel computational methods to understand genomic
structure, ushering in an era of bioinformatics as an independent
discipline (cite).

@@

\begin{figure}
  \centering 
  \caption{This is the pedagogy figure where we explain what is is that the model does }
\end{figure}

@@

\begin{figure}
  \centering 
  \caption{This is the synthetic data figure where we show that our model works with synthetic data across a variety of topologies and geometries}
\end{figure}

@@

\begin{figure}
  \centering 
  \caption{Mouse retina data}
\end{figure}

@@

\begin{figure}
  \centering 
  \caption{C elegans data}
\end{figure}

@@

\begin{figure}
  \centering 
  \caption{Microprocessor data}
\end{figure}

@@

>>>>

\documentclass{nature}
\usepackage[english,american]{babel}
\usepackage{subfiles}
\usepackage{grffile}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{fullpage}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage[citestyle=authoryear,url=false,hyperref=auto,isbn=false]{biblatex}
\addbibresource{connectomics motif.bib}
\addbibresource{connectomics motif-relational models.bib}

\DeclareGraphicsRule{.ai}{pdf}{.ai}{}

\title{Discovering cell type motifs in connectomics data}
\author{Eric Jonas, Konrad Kording}

@@

% \begin{affiliations}
%   \item Something Something
%   \item Something Something
% \end{affiliations}

@@

\section*{Introduction}
Emerging techniques (cite Lichtman, Zador, Denk etc) promise to
quantify the location of each neuron within a volume of interest,
along with its connections to all other neurons. Far exceeding the
capacity of neuroanatomists to trace small circuits, this leads to
enormous datasets that quantify aspects of the nervous system. The
rise of high-throughput sequencing techniques necessitated the
development of novel computational methods to understand genomic
structure, ushering in an era of bioinformatics as an independent
discipline (cite).

@@

\begin{figure}
  \centering 
  \centerline{\includegraphics[width=8.5in]{overview.ai}}
  \caption{This is the pedagogy figure where we explain what is is
    that the model does. }
\end{figure}

@@

\begin{figure}
  \centering 
  \centerline{\includegraphics[width=8.5in]{synthetic.ai}}
  \caption{This is the synthetic data figure where we show that our model works with synthetic data across a variety of topologies and geometries}
\end{figure}

@@

\begin{figure}
  \centering 
  \centerline{\includegraphics[width=8.5in]{mouseretina.ai}}
  \caption{Mouse retina data}
\end{figure}

@@

\begin{figure}
  \centering 
  \centerline{\includegraphics[width=8.5in]{celegans.ai}}
  \caption{C elegans data}
\end{figure}

@@

\begin{figure}
  \centering 
  \centerline{\includegraphics[width=8.5in]{mos6502.ai}}
  \caption{Microprocessor data}
\end{figure}

@@

\begin{addendum}
 \item Put acknowledgements here.
 \item[Competing Interests] The authors declare that they have no
competing financial interests.
 \item[Correspondence] Correspondence and requests for materials
should be addressed to A.B.C.~(email: myaddress@nowhere.edu).
\end{addendum}
